Automated Example Oriented REST API Documentation

### 2017-11-08 appendix.tex
adds the copyright info
adds ethics certificate
overview + questionnaire

>>>>

\chapter{Permissions for Reusing Published Papers in PhD Thesis}

\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{copyrights/services.pdf}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{copyrights/spy_rest.pdf}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{copyrights/tool.pdf}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{copyrights/cisco_paper.pdf}
\end{figure}
\chapter{Ethics Certificate}
\label{ethics}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{ethics.pdf}
\end{figure}
\chapter{API Tasks for Controlled Study}
\label{chap:appendix_questions}
\begin{enumerate}
  \item \textbf{List all Posts.} Use the WordPress REST API to get a list of all the blog posts from the blog at http://wp.spyrest.com"
  \item \textbf{Find all posts by author Spyrest.} Use the WordPress REST API to find a list of all the blog posts by author Spyrest from the blog at http://wp.spyrest.com"
  \item \textbf{List all Posts excluding ids 1 and 4} Use the WordPress REST API to find a list of all the blog posts where the post id is not 1 or 4 from the blog at http://wp.spyrest.com"
  \item \textbf{Find the total number of Posts.} Use the WordPress REST API to find the total number of blog posts from the blog at http://wp.spyrest.com"
  \item \textbf{Publish a Post} Use the WordPress REST API to publish a new post with title 'a random post', content 'lorem ipsum' and published date of 'January 1, 2016' on the blog at http://wp.spyrest.com"
  \item \textbf{Update the excerpt of the Post you published to 'My new excerpt'.} Use the WordPress REST API to update the excerpt for the post you created from the blog at http://wp.spyrest.com."
\end{enumerate}

\chapter{Feedback Questionnaire for Controlled Study}

\begin{enumerate}
  \item Rate your experience of performing the API tasks using the \textbf{WordPress REST API} documentation (10 being the best possible).
  \item Share your thoughts about the reasoning behind the above rating.
\end{enumerate}

### 2017-11-08 introduction.tex
adds box borders
overview + questionnaire

While there are overlaps between the documentation requirements of local and REST APIs, there are significant requirements that are unique to each. The differences between the documentation
of local vs. REST APIs can be depicted by an example as follows:
\newcommand*{\captionsource}[2]{%
  \caption[{#1}]{%
    \textbf{Source:} #2%
    \\\hspace{\linewidth}%
    #1%
  }%
}
\begin{figure}[htb]
  \includegraphics[width=\linewidth]{javadoc.png}
  \captionsource{Example Local API Documentation from Formatted Comments Using JavaDoc}{Log4J}
  \label{fig:javadoc}
\end{figure}

@@

\begin{figure}[htb]
  \includegraphics[width=\linewidth]{wordpress_doc.png}
  \captionsource{Difference between a REST API Code and its Documentation}{WordPress REST API}
  \label{fig:wordpress_doc}
\end{figure}

@@

\section{Cohesion and Unitary Report}
To address the aforementioned research goals and objectives, my research strategy included five sub-projects, which have resulted in publications at peer-reviewed international conferences. Table~\ref{table:chapter_summary} shows a high level overview of the flow of arguments between the sub-projects to meet the research goals and questions.

\begin{table}
  \caption{Summary and Flow of Arguments of the Sub-projects}
  \begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{4.5cm}|p{6cm}|}
  \hline
  Chapter & Goal & Question& Research Project & Primary Outcome \\
  \hline
  Chapter~\ref{chapter:case_study}  & RG1 & RQ1 & A case study of Web API evolution \cite{sohan2015case}. & A set of challenging problems related to evolving Web APIs. Selected REST API documentation as the problem of interest for this research. \\
  \hline
  Chapter~\ref{chapter:spy_rest} & RG1 and RG2 & RQ2 and RQ3 & SpyREST: Automated RESTful API documentation using an HTTP proxy server \cite{sohan2015spyrest}. & A list of requirements. A conceptual design using interception to generate REST API documentation to meet the requirements. \\
  \hline
  Chapter~\ref{chapter:demo_paper} & RG2 & RQ3 & SpyREST in action: An automated RESTful API documentation tool \cite{sohan2015spyrest_tool}. & A reusable tool that implements the conceptual design and shows how the identified REST API documentation requirements are met.\\
  \hline
  Chapter~\ref{chapter:cisco_study} & RG2 & RQ4 & Automated example oriented REST API documentation at Cisco \cite{sohan_cisco}. & Empirical evidence that the proposed technique provides a practical documentation solution for REST API developers.\\
  \hline
  Chapter~\ref{chapter:controlled_study} & RG2 & RQ5 & A study of the effectiveness of usage examples in REST API documentation \cite{sohan_vlhcc}. & Empirical evidence that the proposed technique allows REST API client developers to perform API tasks with less effort, higher success and satisfaction ratings.\\
  \hline
\end{tabular}
\label{table:chapter_summary}
\end{table}

>>>>

While there are overlaps between the documentation requirements of local and REST APIs, there are significant requirements that are unique to each. The differences between the documentation
of local vs. REST APIs can be depicted by an example as follows:
\newcommand*{\captionsource}[2]{%
  \caption[{#1}]{%
    \textbf{Source:} #2%
    \\\hspace{\linewidth}%
    #1%
  }%
}
\begin{figure}[htb]
  \fbox{\includegraphics[width=\linewidth]{javadoc.png}}
  \captionsource{Example Local API Documentation from Formatted Comments Using JavaDoc}{Log4J}
  \label{fig:javadoc}
\end{figure}

@@

\begin{figure}[htb]
  \fbox{\includegraphics[width=\linewidth]{wordpress_doc.png}}
  \captionsource{Difference between a REST API Code and its Documentation}{WordPress REST API}
  \label{fig:wordpress_doc}
\end{figure}

@@

\section{Cohesion and Unitary Report}
To address the aforementioned research goals and objectives, my research strategy included five sub-projects, which have resulted in publications at peer-reviewed international conferences. Figure~\ref{fig:flow} and Table~\ref{table:chapter_summary} show a high level overview of the flow of arguments between the sub-projects to meet the research goals and questions.

\begin{figure}[htb]
  \includegraphics[width=\linewidth]{flow.png}
  \caption{Overview of Flow of Arguments of the Sub-Projects }
  \label{fig:flow}
\end{figure}

\begin{table}
  \caption{Summary of the Sub-projects}
  \begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{4.5cm}|p{6cm}|}
  \hline
  Chapter & Goal & Question& Research Project & Primary Outcome \\
  \hline
  Chapter~\ref{chapter:case_study}  & RG1 & RQ1 & A case study of Web API evolution \cite{sohan2015case}. & A set of challenging problems related to evolving Web APIs. Selected REST API documentation as the problem of interest for this research. \\
  \hline
  Chapter~\ref{chapter:spy_rest} & RG1 and RG2 & RQ2 and RQ3 & SpyREST: Automated RESTful API documentation using an HTTP proxy server \cite{sohan2015spyrest}. & A list of requirements. A conceptual design using interception to generate REST API documentation to meet the requirements. \\
  \hline
  Chapter~\ref{chapter:demo_paper} & RG2 & RQ3 & SpyREST in action: An automated RESTful API documentation tool \cite{sohan2015spyrest_tool}. & A reusable tool that implements the conceptual design and shows how the identified REST API documentation requirements are met.\\
  \hline
  Chapter~\ref{chapter:cisco_study} & RG2 & RQ4 & Automated example oriented REST API documentation at Cisco \cite{sohan_cisco}. & Empirical evidence that the proposed technique provides a practical documentation solution for REST API developers.\\
  \hline
  Chapter~\ref{chapter:controlled_study} & RG2 & RQ5 & A study of the effectiveness of usage examples in REST API documentation \cite{sohan_vlhcc}. & Empirical evidence that the proposed technique allows REST API client developers to perform API tasks with less effort, higher success and satisfaction ratings.\\
  \hline
\end{tabular}
\label{table:chapter_summary}
\end{table}
